14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-12 rules/rules19.tex
Rules: More TODOs.

\header{System description.}
%
As part of the submission, SMT-COMP entrants are \emph{required} to provide a
short (1–-2 pages) description of the system.  This should include a list of
all authors of the system, their present institutional affiliations, and any
appropriate acknowledgements.  The programming language(s) and basic SMT
solving approach employed should be described (e.g., lazy integration of a
Nelson-Oppen combination with SAT, translation to SAT, etc.).  System
descriptions should also include a URL for a web site for the submitted tool.
System descriptions must be submitted until the final solver deadline System
descriptions will be made publicly available. \todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}

@@

\header{Wrapper tools.}
%
\todo{Giles: update}
A \emph{wrapper tool} is defined as any solver that calls (or is in
some other way based on) one or more SMT solvers not written by the
author of the wrapper tool.  The other solvers are called the
\emph{wrapped} solvers.  A wrapper tool must explicitly acknowledge
any solvers that it wraps.  Its system description should make clear
the technical innovations by which the wrapper tool expects to improve
on the wrapped solvers.

>>>>

\header{System description.}
%
\todo{add minimum requirement for authorship?}
As part of the submission, SMT-COMP entrants are \emph{required} to provide a
short (1–-2 pages) description of the system.  This should include a list of
all authors of the system, their present institutional affiliations, and any
appropriate acknowledgements.  The programming language(s) and basic SMT
solving approach employed should be described (e.g., lazy integration of a
Nelson-Oppen combination with SAT, translation to SAT, etc.).  System
descriptions should also include a URL for a web site for the submitted tool.
System descriptions must be submitted until the final solver deadline System
descriptions will be made publicly available. \todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}

@@

\header{Wrapper tools.}
%
\todo{Giles: update}
\todo{reword? "one or more SMT solvers of which the author of the wrapper tool
is not an author"}
A \emph{wrapper tool} is defined as any solver that calls (or is in
some other way based on) one or more SMT solvers not written by the
author of the wrapper tool.  The other solvers are called the
\emph{wrapped} solvers.  A wrapper tool must explicitly acknowledge
any solvers that it wraps.  Its system description should make clear
the technical innovations by which the wrapper tool expects to improve
on the wrapped solvers.
